\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Add paragraph for UBIFS.

\subsection{UBIFS}
TODO

>>>>

\subsection{UBIFS}
UBIFS is the Linux Kernel's File System typically used in the Embedded Device
Market, where raw flash chips are used as opposed to traditional Hard Disk
Drives or Solid State Disks.\\
UBIFS also has the capability of authenticating the File System. Similar to
what is proposed for BTRFS in this paper, UBIFS is using a HMAC to protect
it's internal on-disk data structures as well as the file data stored on the
File System.
